### 2014-11-27 tex/short_2015/body.tex
tex additions and comment in autoProxy.vs

A first approximation is for the client to assume that the corresponding part of
the server's model is planar in a region around the given point. If this is the
case, a local 2D texture transformation will provide a good approximation to the
intra-splat texturing to be performed on the client. For the splat centered in
$\vv_{i, j} = (x_j, y_i, z_{i, j})$, to be centered on the client's canvas at
$\pv_{i, j} = P_c M_c M_s^{-1} P_s^{-1}\vv_{i, j}$, the texture coordinate
transformation to be used is,
\[
  T = \ldots,
\]
such that the client fragment $\pv_{i, j} + \delta_{i, j}$ gets texel
\[
  I_{p, q},
\]
with $(p, q) = \ldots$.

>>>>

\vspace{10cm}

A first approximation is for the client to assume that the corresponding part of
the server's model is planar in a region around the given point. If this is the
case, a local 2D texture transformation will provide a good approximation to the
intra-splat texturing to be performed on the client. For the splat centered in
$\vv_{i, j} = (x_j, y_i, z_{i, j})$, to be centered on the client's canvas at
screen coordinate $\pv_{i, j} = P_c M_c M_s^{-1} P_s^{-1}\vv_{i, j} = U\vv_{i,
j}$, the texture coordinate transformation to be used is,
\[
  T =
  \begin{pmatrix} 1/\text{splats}_x & 0 \\ 0 & 1/\text{splats}_y \end{pmatrix}
  \Big( \sv_x \, \, \, \sv_y \Big)^{-1}
  \begin{pmatrix} \text{vpwidth}/\text{splats}_x & 0 \\ 0 & \text{vpheight}/\text{splats}_y \end{pmatrix}
  \cdot \text{overlap},
\]
where $(\ev_1 \, \, \, \ev_2)$ maps the ``client's splat region'' (in $[0,
1]^2$) to the corresponding texture area, $(\sv_{dx} \, \, \, \sv_{dy})^{-1}$
maps the ``client's screen space splat area'' to $[0, 1]^2$, and $\text{splatSize}_x
= \text{vp}_\text{width}/\text{splats}_x$ and $\text{splatSize}_y
= \text{vp}_\text{height}/\text{splats}_y$ together with the ``overlap'' just
provides a scaling factor so that ``overlap=1'' produces non-overlapping but
covering splats when $M_c=M_s$, \ie, the client does no transformation of the
proxy model.

We compute $\sv_{dx}$ and $\sv_{dy}$ by sampling proxy model positions and
performing the perspective division and transformation into window coordinates
in the vertex shader.
Let
\[
  \text{pos} =
  U { \small \begin{pmatrix} x \\ y \\ d \\ 1 \end{pmatrix} },
  \text{pos}_{\Delta x} =
  U { \small \begin{pmatrix} x+\Delta x \\ y \\ d_{\Delta x} \\ 1 \end{pmatrix} }
  \text{and}\, \, \, 
  \text{pos}_{\Delta y} =
  U { \small \begin{pmatrix} x \\ y+\Delta y \\ d_{\Delta y} \\ 1 \end{pmatrix} },
\]
where $d = 2\text{depthTex}(x, y) - 1$, $d_{\Delta x} =
2\text{depthTex}(x+\Delta x, y) - 1$, and $d_{\Delta y} = 2\text{depthTex}(x,
y+\Delta y) - 1$ are depths sampled from the received depth buffer and transformed
to $[-1, 1]$.

We use $\Delta = \Delta x = \Delta y = ...$, so that ...

Then, for the 2D vectors spanning the splats in client window coordinates, we
get
\[
  \sv_{\Delta x} =
    \frac{\text{viewport width}}{2\Delta x} \left(
        \frac{\text{pos}_{\Delta x}.xy}{\text{pos}_{\Delta x}.w} -
        \frac{\text{pos}.xy}{\text{pos}.w}
    \right),
\]
and
\[
  \sv_{\Delta y} =
    \frac{\text{viewport width}}{2\Delta y} \left(
        \frac{\text{pos}_{\Delta y}.xy}{\text{pos}_{\Delta y}.w} -
        \frac{\text{pos}.xy}{\text{pos}.w}
    \right),
\]
where we have used the ``shader notation'' to extract 2D vectors and scalars
from the 4D vectors.

Then, ...

such that the client fragment $\pv_{i, j} + \delta_{i, j}$ gets texel
\[
  I_{p, q},
\]
with $(p, q) = \ldots$.
